Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-23 paper.tex
update

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method. we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using our proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) used in our PSO-based approach, we set the parameters settings for the GP-based approach using 30 individuals and 100 generations.

>>>>

\subsection{Comparison Test for GP-based approach and PSO-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO-based method. we consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using our proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) used in our PSO-based approach, we set the parameters settings for the GP-based approach using 30 individuals and 100 generations.
